Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-15 analysis/paper/paper.Rmd
Clean up/clarify journal titles included table caption

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>%
  rename(Journal = journal,
         `IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  fontsize(size = 10, part = "body") %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  set_caption(
    "Journal titles selected for inclusion, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
  )
```

>>>>

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>%
  rename(Journal = journal,
         `IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  fontsize(size = 10, part = "body") %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  set_caption(
    "Journal titles selected for inclusion representing 21 plant pathology journals or specialised journals featuring plant pathology focused articles, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
  )
```
